Models of lens candidates from Space Warps CFHTLS

### 2017-03-20 parts/intro.tex
editing introduction

All this motivates using galaxy lenses to study the mutual dynamics of
dark matter and gas in galaxies.  Several studies in recent years have
done so
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their masses.
Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016A&A...592A..75P} and by visual inspection
by citizen-science volunteers in Space~Warps
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree.  So one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from the LSST in optical and the SKA in radio on the ground,
and Euclid and WFIRST in orbit.  The expected flood of new lens
discoveries will need a similarly huge modelling effort to reconstruct
their mass distributions.

To prepare for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in lens discovery through Space~Warps, as well as
several other projects involving astronomical data.

In this paper, we present SpaghettiLens models of lens-candidates discovered through Space~Warps.
Its purpose is twofold.
First to check if the created models look like plausible lenses and whether the shortcomings diagnosed in \cite{2015MNRAS.447.2170K} were fixed.
Second to introduce diagnostic criteria that help filter out the most probable lens candidates and the possibly most rewarding for future follow up observations.
While introducing these diagnostic criteria, we also gain some preliminary estimations of some properties of the lens-candidates as galaxies.

>>>>

All this motivates using galaxy lenses to study the mutual dynamics of
dark matter and gas in galaxies.  Several studies in recent years have
done so
\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
enlarge the samples from tens of lensing galaxies to thousands.  Doing
so requires both finding more lenses and also modelling their masses.
Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
arc-finders
\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
machine learning \citep{2016A&A...592A..75P} and by visual inspection
by citizen-science volunteers in Space~Warps
\citep{2016MNRAS.455.1191M} have, between them, discovered an average
of four lenses per square degree.  So one can be optimistic about
finding many thousands of lenses in the next generation of wide-field
surveys, from the LSST in optical and the SKA in radio on the ground,
and Euclid and WFIRST in orbit.

The expected flood of new lens discoveries will need a similarly huge
modelling effort to reconstruct their mass distributions.  To prepare
for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in lens discovery through Space~Warps, as well as
several other projects involving astronomical data.  This paper
continues by applying SpaghettiLens to lens-candidates discovered
through Space~Warps.  We present results from modelling of 42 of the
59 lens candidates reported by \cite{2016MNRAS.455.1191M}.

The aim of this work is twofold.  First, one would like to identify
the most probable lens and the systems likely to be most rewarding for
future follow-up observations.  For this we introduce some
diagnostics; these

  Its purpose is twofold.  First to check if the
created models look like plausible lenses and whether the shortcomings
diagnosed in \cite{2015MNRAS.447.2170K} were fixed.  Second to
introduce diagnostic criteria that help filter out   While introducing these diagnostic criteria, we also
gain some preliminary estimations of some properties of the
lens-candidates as galaxies.
